Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-04-30 scnn.tex
end of the day

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx,array}
\usepackage{amsmath}
\usepackage{siunitx}

@@

@@

Following~\cite{shuman2013emerging}, the graph normalized graph Laplacian
defined as $L = I - D^{-1/2} W D^{-1/2}$ is a second order differential operator
that can be used to define the graph Fourier basis. Here $D$ is the diagonal
matrix where $D_{ii}=d_i$. The graph Fourier basis is defined as the harmonic
decomposition of the graph Laplacian $L=U \Lambda U^*$, where $U$ is the
orthonormal matrix of eigenvectors and $\Lambda$, the diagonal matrix of
eigenvalues.

@@

Convolution

>>>>

%% The amssymb package provides various useful mathematical symbols
\usepackage{amssymb}
\usepackage{color}
\usepackage{url}
\usepackage{hyperref}
\usepackage{graphicx,array}
\usepackage{amsmath}
\usepackage{siunitx}
\usepackage{bm}

@@

\renewcommand{\b}[1]{{\bm{#1}}}   % bold symbol

% MATH SYMBOLS
\newcommand{\1}{\b{1}}              % all-ones vector
\newcommand{\0}{\b{0}}              % all-zero vector
\newcommand{\g}[1]{\b{#1}}
\renewcommand{\L}{\b{L}} % the laplacian matrix
\newcommand{\W}{\b{W}} 
\newcommand{\I}{\b{I}} 
\newcommand{\D}{\b{D}} 
\newcommand{\U}{\b{U}}
\newcommand{\bLambda}{\b{\Lambda}} 
\newcommand{\blambda}{\b{\lambda}}

@@

Following~\cite{shuman2013emerging}, the graph normalized graph Laplacian
defined as $\L = \I - \D^{-1/2} \W \D^{-1/2}$ is a second order differential operator
that can be used to define the graph Fourier basis. Here $D$ is the diagonal
matrix where $\D_{ii}=\b{d}_i$. By construction the Laplacian is symetric postive
semi-definite and hence can be decomposed as $\L=\U \bLambda \U^*$, where $U$ is an
orthonormal matrix of eigenvectors and $\bLambda$, the diagonal matrix of
eigenvalues. The graph Fourier basis is defined as the Laplacian eigenvectors.
The graph Fourier transform of $f$ is simply its projection on $U$ given by 
$\hat{\b{f}}=\U^*\b{f}$. Similarly the inverse graph Fourier transform reads $\b{f}=\U\hat{\b{f}}$.
Note that instead of frequencies, the Fourier modes are crescently ordered with
respect of the Laplacian eigenvalues $\bLambda$. In a sense, the Laplacian
eigenvalues correspond to the squared frequencies.

@@

Graph convolution is defined by generalizing the concept that convolution is a
multiplication in the spectral domain. Given a convolution kernel 
$h:\mathbb{R}_+\rightarrow\mathbb{R}$, the convolution of a signal $\b{f}$ 
is defined as
\begin{equation} \label{def:graph_convolution}
h(L)\b{f} = \U h(\bLambda) \U^* \b{f},
\end{equation}
where $h(\bLambda)$ is a diagonal matrix where $h(\bLambda)_{ii}=h(\bLambda_{ii})$.
Equation~\ref{def:graph_convolution} contains three parts: a) $\U^* \b{f}$, the 
Fourier transform of $\b{f}$; b) $h(\bLambda)$ the multiplication with the Fourier 
kernel $h(\blambda)$; and c) $\U$ the inverse Fourier transform.

The major difference with classical convolution is that the convolution kernel
$h$ cannot be thought as $n \times n$ pattern, but is a continuous function
applied to the graph eigenvalues $\bLambda$. For visualization puposes, one can
look at effect of the convolution on a dirac, i.e. one column of the matrix
$h(\L)$. \nati{However, due to the non regularity of the graph (i.e. the fact
that there is not perfect sampling on the sphere), this visualization will
differ from one node to another. In the specific case of the full sphere, these
difference are negligible in most of the cases. When considering only subpart of
the sphere, one will observe important border effects.}

\paragraph{Example: heat diffusion}
Let us consider the heat diffusion problem 
\begin{equation} \label{eq:heat_equation}
\L \b{f}(t) = \tau \partial_t \b{f}(t),
\end{equation}
where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition 
$\b{f}(0)$, the solution of~\ref{eq:heat_equation} can be expressed as
\begin{equation}
\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U^* \g{f}(0) = K_t(\L) \b{f}(0), 
\end{equation}
which is a convolution of the signal $\b{f}(0)$ with the kernel 
$K_t(x)=e^{-\tau t x}$. Here the kernel $K_t$ is applied to the correspond
In Figure~\ref{fig:gaussian_filters_comparizon}, we show the effect of the convolution by diffusing a unit of heat for various amount of time.
